Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-11 main.tex
DI done

@@

>>>>

Figure~\ref{fig:KS1} shows the inference rule for the deep inference
system~$\FOKS$ that we are using this paper. It is a slight variation
of the systems presented by Br\"unnler~\cite{brunnler:phd} and
Ralph~\cite{ralph:phd} in their PhD-theses. The main differences being
that we (i) the explicit presence of the $\mixr$-rule, (ii) a
different choice of how the formula equivalence $\fequ$ is defined,
and (iii) an explicit rule for the equivalence.

We consider here only the cut-free fragment, as cut-elimination for
deep inference systems has already been discussed
elsewhere~\cite{brunnler:,alertubella:}.\footnote{In the deep
inference literature, the cut-free fragment is also called the
\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
here, we omit the down-arrows $\downarrow$ in the rule names.}

As with the sequent system $\FOLK$, we also need for $\FOKS$ the
\emph{linear fragment}, that we call here $\FOMLS$, and that is shown
in Figure~\ref{fig:KS1} in the dashed box.

@@

We are now ready to see the main results of this paper.
